Automatic Matching of Bullet Lands

### 2015-12-29 imaging-paper.Rnw
shading of ROC curves

rocs$variable <- reorder(rocs$variable, -rocs$auc, min)
qplot(`FALSE`, `TRUE`, data=subset(rocs, auc > 0.5),  geom="line", group=type) + theme_bw() + geom_abline(linetype=2) + xlab("False negative rate") + 
  ylab("False positive rate") + facet_wrap(facets=~variable, ncol=4) + 
  geom_label(x=1, y=0, aes(label=labels), data=labels, hjust=1, vjust=0)
@
\caption{\label{fig:rocs}ROC curves for all of the features described in section~\ref{sec:algorithm}. Variables are sorted according to their area under the curve (AUC). Except for the distance $D$ between signatures, all features are more predictive than the maximal CMS. }
\end{figure}

>>>>

ggplot(roc.data, aes(x=fpr, ymin=0, ymax=tpr)) +
    geom_ribbon(alpha=0.2) +
    geom_line(aes(y=tpr)) +
    ggtitle(paste0("ROC Curve w/ AUC=", auc))

rocs$variable <- reorder(rocs$variable, -rocs$auc, min)
ggplot(data=subset(rocs, auc > 0.5)) +
  geom_ribbon(aes(x=`FALSE`, ymax=`TRUE`, ymin=0), alpha=0.2) +
  geom_line(aes(x=`FALSE`,y=`TRUE`))+ theme_bw() + xlab("False negative rate") + 
  ylab("False positive rate") + facet_wrap(facets=~variable, ncol=4) + 
  geom_label(x=1, y=0, aes(label=labels), data=labels, hjust=1, vjust=0) + 
  geom_abline(linetype=2)
@
\caption{\label{fig:rocs}ROC curves for all of the features described in section~\ref{sec:algorithm}. Variables are sorted according to their area under the curve (AUC). Except for the distance $D$ between signatures, all features are more predictive than the maximal CMS. }
\end{figure}
